---
title: 'Assignment 5: Calibration'
author: "Mia Guarnieri, Lauren Harris, Alia Ajina"
date: "2023-05-11"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
    code_folding: show
    smooth_scroll: yes
    collapsed: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Installing required packages
library(sensitivity)
library(tidyverse)
library(lubridate)
library(reldist)
library(purrr)
library(ggpubr)
library(here)
```

## Testing new metric 

Modeled - observed drought days

```{r drought days}
# Read in sager data
sager <- read.table("../Data/sager.txt", header=T)

# Add and mutate data
sager = sager %>% mutate(date = paste(day,month,year, sep="/"))
sager$date = as.Date(sager$date,"%d/%m/%Y")

# Sourcing our function
source(here("R", "drought_days.R"))

# Testing our function
dd_test <- drought_days(sager)
```

## Creating and calibrating combined metric

Sum of correlation between modeled and observed wet days and modeled and observed dry days. Min = 0 (no correlation of modeled and observed data for either wet or dry days) max = 2 (perfect correlation of modeled and observed data for both wet and dry days)

```{r combined metric}

source(here("R", "combined_metric.R"))

cm <- combined_metric(m = sager$model, obs = sager$obs, wy = sager$wy)

# Read in msage data
msage <- read.table("../Data/sagerm.txt", header=T)

# Organize msage data
nsim = ncol(msage)
snames = sprintf("S%d",seq(from=1, to=nsim))
colnames(msage) = snames

# Use date from our earlier output
msage$date = sager$date
msage$month = sager$month
msage$year = sager$year
msage$day = sager$day
msage$wy = sager$wy

# Add observed data
msage <- left_join(msage, sager[,c("obs","date")], by = c("date"))

# Creating subset to split the sample calibration
short_msage <- subset(msage, wy < 1975)

# Computing performance measures for output from all parameters
res <- short_msage %>% 
  select(!c("date","month","year","day", "obs", "wy")) %>%
  map_dbl(combined_metric, obs = short_msage$obs, wy = short_msage$wy)

# Determining our best and worst parameter set
# Best parameter set
which.max(res)

# Worst parameter set
which.min(res)
```

## Determination of Best and Worst Parameter Sets

We determined that our best parameter set was S10 and our worst parameter set was S77.
